Long_time_series

### 2019-03-01 Detect_MCSs.Rmd
fixed
study_site
updated

# Time series

The first few lines of this script only looks at a time series of 10 years or greater. However, from line 355 a longer time series is used. This time series has a length of greater than 30 years and so only a few sites are used. With a longer time series I am able to detect for extreme events such as Marine Cold Spells (MCSs).

@@

## OISST dataset
```{r}
# # AVHRR <- read_csv("data/csvavhrr-only-v2-19810901-20180630.csv")
# 
# OISSTDir <- "~/Documents/Masters_2019/Data_SST"
# OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
#             col.names = c("lon", "lat", "temp", "date"))
# 
# #OISST <- as.tibble(fread("~/Documents/Masters_2019/MastersProject/Data/csvavhrr-only-v2-19810901-20180630.csv"))
# # Quick visualisation of the data
# # To explore the data I visualise the min temperatures along the South african coastline.
# 
# OISST %>%
#   filter(date == min(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
# ggsave(plot = OISST, filename = "Figures/OISST")
```

>>>>

# Script Info (Time series)

The first few lines of this script only looks at a time series of 10 years or greater. However, from line 360 a longer time series is used. This time series has a length of greater than 30 years and so only a few sites are used. With a longer time series I am able to detect for extreme events such as Marine Cold Spells (MCSs).

@@

## OISST dataset
```{r}
# AVHRR <- read_csv("data/csvavhrr-only-v2-19810901-20180630.csv")

# OISSTDir <- "~/Documents/Masters_2019/Data_SST"
# OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
#             col.names = c("lon", "lat", "temp", "date"))

OISST <- as.tibble(fread("Data/csvavhrr-only-v2-19810901-20180630.csv"))
# # Quick visualisation of the data
# # To explore the data I visualise the min temperatures along the South african coastline.
# 
# OISST %>%
#   filter(date == min(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
# ggsave(plot = OISST, filename = "Figures/OISST")
```
